Modular Model-Checking of a Byzantine Fault-Tolerant Protocol

### 2017-03-01 paper/paper.tex
reviewers: mention the kibitzer is novel.
Fixing issues raised by the reviewers
  * 'c' should be 'cal' in calendar laws (3)
  * send and recv relations are used as relations and notation is abused
    to use them as characteristic functions

Our primary contributions are (1) a model-checking verification of an $\OMH$ implementation, and (2) demonstrating that our modeling paradigm allows for modular verification.

@@

\item \label{cal:d} In all states, if the current time equals a timeout, then the only transitions enabled are calendar event updates associated with the timeout: $\forall \sigma \in S$, $\exists (e_i, t_i) \in \sigma(cal)$ such that $\sigma(now) = t_i$, then $\forall \sigma'$ such that $\sigma \rightarrow \sigma'$, $\sigma'(now) = \sigma(now)$, $\sigma'(c_j) = \sigma(c_j)$ for all $c_j \in \sigma(c)$ such that $c_j \neq c_i$, and $c_i \notin \sigma'(c)$.

@@

Assume processes are indexed from a finite set $\Id$. A \emph{channel} from process $i$ to $j$ is an ordered pair $(i,j)$. Define a set of messages $\Msg$. Given a channel and a timeout, let $send$ be a relation on messages sent on a channel at a given time:
$$send \subseteq \Id \times \Id \times \mathbb{R} \times \Msg$$
So $send(i, j, t, m)$ holds iff $i$ sends to $j$ message $m$ at time $t$. Likewise, let
$$recv \subseteq \Id \times \Id \times \mathbb{R} \times \Msg$$
be a relation on messages received on a channel at a time, so that $recv(i, j, t, m)$ holds iff the message $m$ received by $j$ from $i$ at time $t$.

In the absence of faults, we require that messages received were previously sent and not previously received: if $recv(i, j, t, m)$, then $\exists t'$ such that $send(i, j, t', m)$ where $t' < t$, and $\neg\exists t''$ such that $t' < t'' < t$ and $recv(i, j, t'', m) = recv(i, j, t, m)$. (We address faults in Section~\ref{sec:kibitzer}.)

@@

The event of receiving a message initiates a process to update its local transition system and generate additional messages to send. When the process is updating its local transition system, the event calendar is paused. That is, updating an event $recv(i, j, t, m)$ also includes updating $j$'s transition system.

>>>>

Our primary contributions are (1) a model-checking verification of an $\OMH$ implementation, and (2) demonstrating that our modeling paradigm allows for modular verification. Additionally, the idea of symbolic fault injection (Section~\ref{sec:kibitzer}) is novel.

@@

\item \label{cal:d} In all states, if the current time equals a timeout, then the only transitions enabled are calendar event updates associated with the timeout: $\forall \sigma \in S$, $\exists (e_i, t_i) \in \sigma(cal)$ such that $\sigma(now) = t_i$ implies $\forall \sigma'$ such that $\sigma \rightarrow \sigma'$, $\sigma'(now) = \sigma(now)$, $\sigma'(c_j) = \sigma(c_j)$ for all $c_j \in \sigma(cal)$ such that $c_j \neq c_i$, and $c_i \notin \sigma'(cal)$.

@@

Assume processes are indexed from a finite set $\Id$. A \emph{channel} from process $i$ to $j$ is an ordered pair $(i,j)$. Fix a set of messages $\Msg$. Given a channel and a timeout, let $send$ be a relation on messages sent on a channel at a given time:
$$send \subseteq \Id \times \Id \times \mathbb{R} \times \Msg$$
So $send(i, j, t, m)$ holds iff $i$ sends to $j$ message $m$ at time $t$. Likewise, let
$$recv \subseteq \Id \times \Id \times \mathbb{R} \times \Msg$$
be a relation on messages received on a channel at a time, so that $recv(i, j, t, m)$ holds iff the message $m$ received by $j$ from $i$ at time $t$.

In the absence of faults, we require that messages received were previously sent and not previously received: if $(i, j, t, m) \in recv$, then $\exists t'$ such that $(i, j, t', m) \in recv$ where $t' < t$, and $\neg\exists t''$ such that $t' < t'' < t$ and $(i, j, t'', m) = (i, j, t, m)$. (We address faults in Section~\ref{sec:kibitzer}.)

@@

The event of receiving a message initiates a process to update its local transition system and generate additional messages to send. When the process is updating its local transition system, the event calendar is paused. That is, updating an event $(i, j, t, m) \in recv$ also includes updating $j$'s transition system.
